The contact value approximation for the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-03-24 papers/pair-correlation/paper.tex
switch to cyan for CVA approximation Tested on darcy. Took 0:21.47.

\newcommand{\plotcomp}[1]{The top halves of these figures show the
  results of Monte Carlo simulations, while the bottom halves show the
  CVA-S.  On the right are plots of #1 on the paths illustrated in the
  figures to the left.  These plots compare the CVA-S (blue) and CVA
  (\fixme{color: change from black?}) with Monte Carlo results (black)
  and the results of Sokolowski and Fischer
  (red)~\cite{sokolowski1992role}, and those of Fischer and Methfessel
  (green)~\cite{fischer1980born}.  The latter is only plotted at
  contact, where it is defined}

>>>>

\newcommand{\plotcomp}[1]{The top halves of these figures show the
  results of Monte Carlo simulations, while the bottom halves show the
  CVA-S.  On the right are plots of #1 on the paths illustrated in the
  figures to the left.  These plots compare the CVA-S (blue solid line) and CVA
  (cyan dotted line) with Monte Carlo results (black circle)
  and the results of Sokolowski and Fischer
  (red dashed line)~\cite{sokolowski1992role}, and those of Fischer and Methfessel
  (green dot-dashed line)~\cite{fischer1980born}.  The latter is only plotted at
  contact, where it is defined}
